\plaintitle

### 2016-08-17 drafts/labor/cases.tex
more topic sentences in cases.tex - see bold in cases.pdf

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}

\section{Major Research Questions}
% \ali{4 paragraphs on what happened in the above contexts; 2 paragraphs on best/worst outcomes \& why; ??? paragraphs on predictions for crowdsourcing}

@@

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  % \item \cref*{sec:decomposition},
  \item \lowercase{\nameref{sec:decomposition}},
  \item \nameref{sec:workAbstraction}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
% As we'll discuss these dimensions,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
%

% stronger topic sentences
% boosterist

\subsubsection{Achieving complexity}\label{sec:decomposition}
Crowdsourcing has explored the decomposition of work for the better part of a decade;
\citeauthor{crowdForgeKittur} specifically
drive at this goal by addressing the possibility of
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.

Much of the research in the space of designing crowd work has
sought to illustrate the potential to take highly creative or skilled work
and generate high--quality results.
Perhaps the most notable case study here can be found in
\citeauthor{foundry}'s \textit{Foundry}, which employed
``flash teams'' to accomplish work typically thought of as only within reach of experts
\cite{foundry}.

Research exploring the decomposition of work more generally
--- that is, without the constraint of an employer/requester directing workers ---
has since emerged as well.
\citeauthor{selfsourcingTeevan2014} further push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the [scientific] management of the self as a worker
--- of sorts ---
will prove relevant as we trace the literature surrounding piecework.

The work described thus far has explored along myriad paths the ways that
we can manage workers for the purpose of accomplishing complex tasks with
rapidly sourced workers from all over the world.
Critically, the work's defining characteristic involves
the use of the Internet as a medium both 
to coordinate workers, as well as to do the work itself.
But research into the ``decomposition'' of work more generally
illustrates the same concepts of work that ``Taylorism''
and scientific management sought to embody
---
\citeauthor{professionalCrowdworkEthics} in particular foresaw this danger
and warned of it in, but they were by no means alone in their warnings
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd}.

Following this thread of work, it may be said that
much of the work in crowdsourcing has found ways of ``vertically slicing'' work
such that each person is responsible for as small a task as can be made reasonable
--- taking a minute of audio, for instance, and transcribing that.
The findings we take away from the crowdsourcing literature might be summed up as
a number of ways
to break tasks down \cite[see][]{selfsourcingTeevan2014,foundry,crowdForgeKittur} and
measuring the costs as they relate to work completion \&
to a lesser extent to workers
\cite[see][]{measuringCrowdsourcingCheng,cheng2015break,crowdworkFuture,professionalCrowdworkEthics}.

Research into piecework has considered the decomposition of work;
\citeauthor{10.2307/23702539} describes piecework in \citeyear{10.2307/23702539} as
``\dots~based on examination of various shop jobs,
which included calculation of the standard time and compensation for each task.
Most piecework plans required additional clerical and supervisory people
(such as piecework clerks, inspectors, and ``experts'')\dots'',
allowing for what the \textit{American Machinist} would later call ``paper efficiency'',
describing savings on paper that are in fact passed on to workers
\cite{10.2307/23702539}.
In this context,
the introspection of tasks by experts and the careful work assignment \& management of workers
we see in historical piecework seem to parallel crowdsourcing.

% \citeauthor{Brown01041990} draws more decisive boundaries on piece rate approaches to remuneration,
identifying in analysis of data from
the U.S. Bureau of Labor and Statistics that
``larger establishment are less likely to use piece rates and predominantly female establishments more likely to do so; unionized establishments make significantly greater use of standard--rate pay than do nonunion establishments; \textbf{incentive pay is less likely in jobs with a variety of duties than in jobs with a narrow set of routinized duties}; and the ease of monitoring work quality is correlated with the use of incentive pay''
% \cite{Brown01041990}.

@@

\subsubsection{Work Abstraction}\label{sec:workAbstraction}
Decomposition allows requesters to assign parallelized tasks
without undue concern for the broader context of the work.
The earlier example of transcribed audio is admittedly a carefully curated one
--- used to illustrate the ability
to parallelize work across as many workers as there are tasks ---
but even in this case problems arise;
breaking an hour--long interview into
3,600 1--second--long tasks would seem to make it impossible to do the tasks
for lack of \textit{context},
but the other extreme (one hour--long block)
offers no performance improvement over conventionally sourced work.

@@

    \subsubsection{External Management}
    We discussed Fordism and Taylorism earlier in our discussions of
    \nameref{sec:decomposition} and \nameref{sec:flexibility},
    but here the core of these paradigmatic views
    --- the scientific management of work ---
    becomes relevant.
    We use ``external'' here instead of ``scientific'', however,
    to more broadly capture the disconnect between managers and workers.
    By describing it as thus,
    we can touch on the relationship that workers have with \textit{researchers}, as well,
    even though that work is not strictly
    --- or just not exclusively ---
    of the same nature as the management and experience as when interacting with requesters.

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Major Research Questions}
% \al¬i{4 paragraphs on what happened in the above contexts; 2 paragraphs on best/worst outcomes \& why; ??? paragraphs on predictions for crowdsourcing}

@@

The exploration of crowdsourcing's potential and limits has principally looked at
manipulating and extending along three dimensions:
\begin{inlinelist}
  % \item \cref*{sec:Complexity},
  \item \nameref{sec:Complexity},
  \item \nameref{sec:Slicing}, and
  \item \nameref{sec:flexibility}
\end{inlinelist}.
We'll explore these aspects of crowdsourcing,
discussing the extents to which work can be
decomposed,
contextually abstracted, and
made more resilient to attrition of various forms.
We'll also point to corresponding piecework literature addressing these aspects.
Finally, we'll discuss how these elements will serve
to constrain the upper and lower bounds of crowdsourcing as it relates
to the question of the furthest limits of crowdsourcing.

%      _                                          _ _   _             
%   __| | ___  ___ ___  _ __ ___  _ __   ___  ___(_) |_(_) ___  _ __  
%  / _` |/ _ \/ __/ _ \| '_ ` _ \| '_ \ / _ \/ __| | __| |/ _ \| '_ \ 
% | (_| |  __/ (_| (_) | | | | | | |_) | (_) \__ \ | |_| | (_) | | | |
%  \__,_|\___|\___\___/|_| |_| |_| .__/ \___/|___/_|\__|_|\___/|_| |_|
%                                |_|                                  
%
% stronger topic sentences
% boosterist (???)

\subsubsection{Achieving greater complexity}\label{sec:Complexity}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{Lasecki:2013:CCC:2501988.2502057} tackle an area of computationally assisted interaction
--- conversational artificial intelligence ---
and find ways to arrange workers and formulate a ``crowd--powered conversational assistant''
\cite{Lasecki:2013:CCC:2501988.2502057}.
Other work has followed a similar pattern,
identifying target milestones in Computer Science
that have presented significant challenges for researchers,
and demonstrating that ``crowd--powered'' systems can tackle many of these challenges
with generally greater success than purely computational attempts
\cite[][and others]{Lasecki:2013:RCL:2441776.2441912,foundry}.

% NEEDS TO GO ELSEWHERE
% \citeauthor{cheng2015break} found that microtasks
% --- though not necessarily \textit{faster} than ``macrotasks'' ---
% yield higher quality work,
% particularly when that work is susceptible to frequent interruptions
% \cite{cheng2015break}.

\topic{While much of the above work has focused on
clever arrangements of systems to manage collectives of workers,
another body of work has turned inward toward managing the self.}
\citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the [scientific] management of the self as a worker
(of sorts)
will prove relevant as we trace the literature surrounding piecework.

\topic{A smaller but growing body of work has reflected on these bodies of work
and brought to our attention a number of ethical questions surrounding the
increasing complexity of crowdwork and the hazards that increasingly arise.}
\citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
--- working for increasing amounts of time on tasks of growing complexity, only to discover that requesters are not willing to pay,
for instance ---
but these and other dangers range an enormous landscape % too informal?
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

\topic{We summarize the work discussed so far in this way:
% crowdsourcing researchers have attempted to find the characteristics of crowdwork
researchers of crowdsourcing and on--demand labor in general
have attempted to find the characteristics which
enable and stymie successful applications of this form of work,
and how to get past or around these boundaries.}
Whether this work has focused on the self (as in the case of ``selfsourcing'')
or on others (as in \textit{CrowdForge} and \textit{Foundry}),
crowdsourcing literature has generally studied the constituent work
and attempted either to work around or indeed with the limitations of crowdwork to accomplish a difficult task
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.
% Following this thread of work, it may be said that
% much of the work in crowdsourcing has found ways of ``vertically slicing'' work
% such that each person is responsible for as small a task as can be made reasonable
% --- taking a minute of audio, for instance, and transcribing that.
% The findings we take away from the crowdsourcing literature might be summed up as
% a number of ways
% to break tasks down \cite[see][]{selfsourcingTeevan2014,foundry,crowdForgeKittur} and
% measuring the costs as they relate to work completion \&
% to a lesser extent to workers
% \cite[see][]{measuringCrowdsourcingCheng,cheng2015break,crowdworkFuture,professionalCrowdworkEthics}.

\topic{Research into piecework has explored similar limits,
with particularly striking parallels in
the language used to describe factors necessary for piecework to thrive.}
\citeauthor{10.2307/23702539} describe piecework in \citeyear{10.2307/23702539} as
``\dots~based on examination of various shop jobs,
which included calculation of the standard time and compensation for each task.
Most piecework plans required additional clerical and supervisory people
(such as piecework clerks, inspectors, and ``experts'')\dots'',
allowing for what the \textit{American Machinist} would later call ``paper efficiency'',
describing savings on paper that are in fact passed on to workers
\cite{10.2307/23702539}.
In this context,
the introspection of tasks by experts and the careful work assignment \& management of workers
we see in historical piecework seem to parallel crowdsourcing.

\citeauthor{Brown01041990} draws more decisive boundaries on piece rate approaches to remuneration,
identifying in analysis of data from
the U.S. Bureau of Labor and Statistics that
``larger establishment are less likely to use piece rates and predominantly female establishments more likely to do so; unionized establishments make significantly greater use of standard--rate pay than do nonunion establishments; \textit{incentive pay is less likely in jobs with a variety of duties than in jobs with a narrow set of routinized duties}; and the ease of monitoring work quality is correlated with the use of incentive pay''
\cite{Brown01041990}.

@@

\subsubsection{Work Abstraction}\label{sec:Slicing}
Decomposition allows requesters to assign parallelized tasks
without undue concern for the broader context of the work.
The earlier example of transcribed audio is admittedly a carefully curated one
--- used to illustrate the ability
to parallelize work across as many workers as there are tasks ---
but even in this case problems arise;
breaking an hour--long interview into
3,600 1--second--long tasks would seem to make it impossible to do the tasks
for lack of \textit{context},
but the other extreme (one hour--long block)
offers no performance improvement over conventionally sourced work.

@@

    \subsubsection{External Management}
    We discussed Fordism and Taylorism earlier in our discussions of
    \nameref{sec:Complexity} and \nameref{sec:flexibility},
    but here the core of these paradigmatic views
    --- the scientific management of work ---
    becomes relevant.
    We use ``external'' here instead of ``scientific'', however,
    to more broadly capture the disconnect between managers and workers.
    By describing it as thus,
    we can touch on the relationship that workers have with \textit{researchers}, as well,
    even though that work is not strictly
    --- or just not exclusively ---
    of the same nature as the management and experience as when interacting with requesters.

### 2016-08-17 drafts/labor/trackingWork.tex
small notes
more topic sentences in cases.tex - see bold in cases.pdf

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes}
\usepackage[normalem]{ulem}
% \usepackage{url}
% \def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
% \usepackage{multibib}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
% \usepackage{biblatex}
% \usepackage[square,numbers]{jnatbib}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\setlist{nolistsep}

\def\plaintitle{Reexamining Crowd Work: A Historical Framing of On--Demand Labor as Piecework}
\def\plainauthor{All the people (Ali, Margaret, MSB, who else?)}
\def\emptyauthor{}
\def\plainkeywords{Crowdsourcing}
\def\plaingeneralterms{Documentation, Standardization}

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}
\title{\plaintitle}

>>>>

\usepackage{todonotes,txfonts,balance,graphics,color,alphalph,subfiles,appendix}
\usepackage{booktabs,textcomp,microtype,ccicons,enumitem,moreenum,nth,endnotes,cleveref}
\usepackage[normalem]{ulem}
% \usepackage{url}
% \def\UrlOrds{\do\*\do\-\do\~\do\'\do\"\do\-}%
% \usepackage{multibib}
\usepackage[citestyle=numeric,backend=bibtex]{biblatex}
% \usepackage{biblatex}
% \usepackage[square,numbers]{jnatbib}
\usepackage[T1]{fontenc}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage[utf8]{inputenc} % for a UTF8 editor only

@@

\setlist{nolistsep}
\def\plaintitle{Reexamining Crowd Work: A Historical Framing of On--Demand Labor as Piecework}
\def\plainauthor{All the people (Ali, Margaret, MSB, who else?)}
\def\emptyauthor{}
\def\plainkeywords{Crowdsourcing}
\def\plaingeneralterms{Documentation, Standardization}

@@

\newcommand{\onlyinsubfile}[1]{#1}
\newcommand{\notinsubfile}[1]{}
\newcommand{\note}[1]{\footnote{#1}}
\newcommand{\topic}[1]{#1} % don't do anything with \topic sentences; this is just for drafting 
\onlyinsubfile{\renewcommand{\topic}[1]{\textbf{#1}}} % if you're in a subfile, bold the \topic sentences

\begin{document}
\renewcommand{\onlyinsubfile}[1]{}
\renewcommand{\notinsubfile}[1]{#1}
\renewcommand{\note}[1]{\onlyinsubfile{\note{#1}}}
\title{\plaintitle}
